PyQBench: a Python library for benchmarking gate-based quantum computers

### 2023-03-21 txt/manuscript.tex
Remove outrageous pagebreak
Fix typo

	\begin{figure}[h!]
		\centering
		\includegraphics[scale=1.5]{pics/controlled_unitary}

@@

\pagebreak

@@

Finally, we provide the source code of PyQBench on GitHub~\cite{pyqbenchgithub} under on open
source license which will allow users to utilize and extend our package in their
specific applications.

>>>>

	\begin{figure}[h!]
		\centering
		\includegraphics[width=0.8\textwidth]{pics/controlled_unitary}

@@

@@

Finally, we provide the source code of PyQBench on GitHub~\cite{pyqbenchgithub} under an open
source license which will allow users to utilize and extend our package in their
specific applications.
